Group Signatures Meet Anonymous Credentials: Or, How to Build Privacy Preserving Identities with Accountability

### 2022-02-23 prism-backend/research/gsac/uas-model.tex
Just one issue seems to remain in traceability.

\commentwho{Jesus}{I'm trying to define \Sign, \Verify, \Inspect and \Judge such
  that multiple credentials can be used to produce a single signature, proving
  claims over arbitrary subsets of all the credentials owned by a user. \Verify
  and, consequently, \Inspect and \Judge need to receive all the \gpk's.
  \Inspect only requires one inspector's secret key, though, and will thus only
  produce that inspector's
  function of the signature and message (this is to avoid complex interactive
  protocols between many inspectors). This, however, creates a quite annoying
  syntax. It may just be easier to restrict signatures to claims over the
  attributes contained in \emph{one} credential.}

\commentwho{Jesus}{Maybe we could remove the attribute sets \uattrs, \dattrs,
  \tuattrs, \tdattrs, from the syntax, and assume that they are part of the
  signatures and/or credentials. This would certainly lead to a cleaner syntax,
  but, what impact would that have in other definitions, etc? Specifically, can
  we support selective disclosure credentials without them? (if so, \fissue,
  \feval and \finsp would be essential in doing so.); Right now, I am more in
  favour of trying to remove the attribute sets from the definitions, as much
  as possible (and see if we can still support plain selective disclosure).}

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\feval,\finsp)$.] Given global system
  parameters \parm, and two functions \feval and \finsp, an inspector runs
  \OKeyGen to generate its inspecting key pair. The function \feval defines
  requirements that signed message-signature pairs must meet. The function
  \finsp defines the type of utility that will be extractable from those pairs
  that do not meet \feval. Hereafter, we assume that the public part \opk is
  added to the group public key \gpk, along with \feval and \finsp.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\uattrs,\dattrs,
  \ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\dattrs,
  \ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})
  \rangle$.] %
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred from an issuer in the system, on
  attribute set $\uattrs \cup \dattrs$, where the attributes in $\uattrs$ (and
  the ones in the $\tuattrs_i$'s) are kept hidden from the issuer, while those
  in \dattrs (as well as those in the $\tdattrs_i$'s) are revealed. Moreover,
  $\uattrs \cup \dattrs$ must be a subset of $\bigcup_i (\tuattrs_i \cup
  \tdattrs_i)$. In order to get the credential, the user may leverage previously
  obtained credentials $\cred_i$ from a multiset of other issuers (including the
  one to whom a new credential is being requested) with public keys $\gpk_i$.
  Moreover, each credential $\cred_i$ can be used to prove claims over
  undisclosed attributes $\tuattrs_i$. The user outputs the produced credential
  \cred, while the issuer outputs the protocol transcript \utrans for the
  produced credential.
\item[$\sig \gets \Sign(\usk,\msg,\uattrs,\dattrs,
  \ldblbrace (\gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})$.]
  The user with with secret key \usk, who obtained credentials $\cred_i$ from a
  multiset of issuers in the system, produces a signature \sig over message
  \msg. The produced signature proves arbitrary claims over the set of
  disclosed attributes $\bigcup_i \dattrs_i$ and undisclosed attributes
  $\bigcup_i \uattrs_i$, which must be a subset of the corresponding disclosed
  (resp. undisclosed) attributes \tdattrs (resp. \tuattrs) in the credentials
  used to generate the signature.
\item[$1/0 \gets
  \Verify(\sig,\msg,\dattrs, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]
  Checks whether \sig is a valid signature, over message \msg, satisfying
  arbitrary claims over disclosed attributes $\dattrs$, as well as
  potentially other undisclosed attributes endorsed by issuers in the systsem
  with public keys $\bigcup_i \gpk_i$.
\item[$(\y,\iproof)/\bot \gets
  \Inspect(\osk,\trans,\sig,\msg,\dattrs,
  \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.] %
  \commentwho{Jesus}{I do not like this description. It's complicated. This needs
    to be rephrased from scratch.}
  Executed by the inspector with opening key \osk. Receives a signature \sig
  over message \msg, produced by a set of credentials satisfying claims on
  disclosed attributes $\dattrs$, as well as potentially undisclosed
  attributes, all endorsed by a multiset of issuers with public keys $\gpk_i$. 
  If \trans is a valid set of transcripts of the execution of a
  $\langle\Obtain,\Issue\rangle$ interactive protocol where the signer obtained
  the credential associated to the inspector's group%
  \footnote{Note: we are not constraining that the group to which the inspector
    with key \osk belongs to, issued only one of the credentials used to
    generate the signature being inspected.}, then the function outputs
  a value $\y$ derived from the signer's credential and public key, and the
  signed message, as well as a proof of correct inspection.
\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,\dattrs,
  \ldblbrace \gpk_i\rdblbrace_{i \in \Issuers})$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \y,
  obtained by applying \Inspect to the the pair signature \sig over \msg. 
\end{description}

@@

\paragraph{Issuance, evaluation, and inspection private functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are run by users (maybe, on user-private
data) as part of different algorithms in an \UAS scheme. In all cases, the
user has to prove correctness of their computation. We introduce them next,
\todo{and will give concrete examples in \secref{sec:uac-instantiation}.}

\begin{description}
\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
  conditions an issuer requires in order to issue credentials, when receiving
  a request from a user with a set of disclosed attributes \dattrs, and
  undisclosed attributes \uattrs (which need to be kept private from the
  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Governs customized
  conditions to define whether the owner of a user key and set of credentials --
  or, more specifically, credentials encoding certain attributes -- should be
  able to sign certain messages.
\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credentials, signed
  message, and produced signature (or a subset thereof), should be extractable
  by the group inspector.
\end{description}

\todo{\fissue and \feval are not covered in the security definitions! Probably,
  they should go into traceability -- which may need to be generalized into
  unforgeability or something like that.}

\paragraph{Helper Function \Identify.} In addition, we make use of a helper
function \Identify for our non-frameability definition. This function receives
a signature and a user secret key, and determines whether the latter was used
to produce the former. This is in line with previous works on DAA
\cite{bfg+11,cdl16} and group signatures without traditional open functions
\cite{dl21,fgl21,gl19}. More concreltely \Identify function, defined as $1/0
\gets \Identify(\usk,\sig)$, conveys meaning to our non-frameability definition
conditioned on the fact that, given a signature \sig accepted by \Verify,
\Identify returns $1$ for exactly one \usk.

\paragraph{Global Variables.} %
All the honestly generated users (i.e., all honestly generated user key pairs,
since we assume a one-to-one relationship between user and user key pair), as
well as all honestly generated credentials, are assigned identifiers. Week's
typically write as \uid for users' identifiers, and \cid for credentials'. The
adversary can
refer to any individual user or credential using the corresponding identifier --
even though he may not know the actual contents of the key pairs or credentials.
In games that involve challenge user or credential identifiers, we use \cuid and
\ccid to refer to these challenge user/credential.
%
The games, usually through the oracles, keep track of the users (through
set \UK) and credentials (through table \CRED) that are created as a result of
oracle calls by the adversary, as well as the attributes that each credential
is associated (through table \ATTR), and the user to which each credential has
been issued to (through table \OWNR). We use the user and credential identifiers
to reference specific user key pairs, credentials, and credential attributes.
For instance, $\UK[\uid]$ refers to the user key pair corresponding to user
with identifier \uid, $\PUBUK[\uid]$ refers to the public key of that key pair,
and $\PRVUK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
is the set of attributes that was assigned to the credential with identifier
\cid; and $\OWNR[\cid]$ is set to the \uid corresponding to the user that
credential \cid was issued to.
%
Additionally, the games keep track of all honest and corrupt users that have
been generated, through sets \HU and \CU, respectively. They also keep track of
the signatures that have been honestly produced, through the \SIG table. Since
signatures are produced through credentials, the \SIG table is indexed with
{\cid}s. For the anonymity game, we also need to keep track of the challenge
signatures that the adversary has obtained, in order to prevent trivial wins
by allowing any of them to be opened. 
%
All global variables are initially set by the games to empty values (denoted
with $\bot$), and all tables/sets are initialized as empty tables/sets, denoted
with $\emptyset$. Also, for readability, we abuse the syntax as follows: we
write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
$\OWNR[\cid] = \uid$; \todo{Something else?}

\paragraph{Oracles.} %
Oracles are the interface of the adversary with the corresponding games. In
other words: through these oracles, the game environment exposes to the adversary
functionality that could otherwise be executed only by honest parties with
private knowledge -- knowledge that would make the adversary capable of
trivially breaking the security properties formalized in the experiments.
In the game-based definitions of our \GSAC model, we leverage the following
oracles, which are formally defined in \figref{fig:oracles1} and
\figref{fig:oracles2}. Note that we identify issuers and inspectors by the group
identifier.

@@

        \procedure{$\IGEN(\gid,\fissue)$}{%
          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\gid] \gets (\ipk,\isk,\fissue) \\
          \HI \gets \HI \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\
          \pcreturn \ipk \\
        }

@@

        \procedure{$\OGEN(\gid,\feval,\finsp)$}{%
          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\gid] \gets (\opk,\osk,\feval,\finsp) \\
          \HO \gets \HO \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\
          \pcreturn \opk \\
        }

@@

        \procedure{$\ISSUE(\cid,\uid,\gid,\dattrs,
          \ldblbrace (\sgid,\scid,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \\
          \pcind \pcind
          \Issue(\PRVIK[\gid],\PUBUK[\uid],
          \ldblbrace (\GK[\sgid],\tdattrs)\rdblbrace) \rangle \\
          \trans[\cid] \gets \utrans \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
          \pcreturn \top \\          
        }

        \procedure{$\OBTAIN(\cid,\uid,\gid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs, \\
          \hspace*{65pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
          \hspace*{50pt} \adv \rangle \\
          \CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \uattrs, \dattrs) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTISS(\cid,\uid,\gid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\\
          \hspace*{75pt} \ldblbrace (\GK[\sgid],
          \CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],
          \ldblbrace (\GK[\sgid],\tdattrs)
          \rdblbrace ) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\uattrs,\dattrs) \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\msg,\uid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace )$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\sig,\msg,\scid,\uattrs,\dattrs,\sgid) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},
          \tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%          
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
          \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
          \pcind \feval(\PUBUK[\uid_1],\CRED[\scid_1],\msg):
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\cscid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

    \caption{Detailed oracles available in our model (2/2). Oracles for
      obtaining credentials, signatures, and processing them.}
    \label{fig:oracles}
  \end{figure*}
}

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced though a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

>>>>

\commentwho{Jesus}{I'm trying to define \Sign, \Verify, \Inspect and \Judge such
  that multiple credentials can be used to produce a single signature, proving
  claims over arbitrary subsets of all the credentials owned by a user. \Verify
  and, consequently, \Inspect and \Judge need to receive all the \gpk's.
  \Inspect only requires one inspector's secret key, though, and will thus only
  produce that inspector's function of the signature and message (this is to
  avoid complex interactive protocols between many inspectors). This, however,
  creates a quite annoying syntax. If this becomes unmanageable, it may just be
  easier to restrict signatures to claims over the attributes contained in
  \emph{one} credential.}

\commentwho{Jesus}{I'm moving to a syntax that applies arbitrary functions over
  the credentials, at different points (issuance, evaluation, and inspection).
  Concretely, I'm moving away from the selective disclosure type of syntax.
  However, it is my intention that selective disclosure becomes an especial case
  of this. That is, the syntax should support both credentials with plain
  selective attribute disclosure, and ``functional'' credentials.}

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers). Hereafter, we assume that the
  public part \opk is added to the group public key \gpk, along with \finsp.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})
  \rangle$.] %
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred from an issuer in the system, on
  attribute set $\attrs$ plus, possibly, blinded attributes attested by
  previously obtained credentials $\cred_i$, from a multiset of other issuers
  (which may include the one to whom a new credential is being requested) with
  public keys $\gpk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$\sig \gets \Sign(\usk,\msg,\feval,
  \ldblbrace (\gpk_i,\cred_i)\rdblbrace_{i \in \Issuers})$.]
  The user with with secret key \usk, who obtained credentials $\cred_i$ from a
  multiset of issuers in the system, produces a signature \sig over message
  \msg, meeting the conditions defined by \feval. As in \Obtain and \Issue, we
  omit the credentials' group public keys when possible.
\item[$1/0 \gets
  \Verify(\sig,\msg,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]
  Checks whether \sig is a valid signature, over message \msg.
\item[$(\y,\iproof)/\bot \gets \Inspect(\osk,\trans,\sig,\msg,
  \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.] %
  Executed by the inspector with private key \osk. Receives a signature \sig
  over message \msg, produced by a set of credentials endorsed by a multiset of
  issuers with public keys $\gpk_i$. If \trans contains a set of valid
  transcripts corresponding to the $\langle\Obtain,\Issue\rangle$ interactive
  protocol executions that issued one or more credentials used to produced \sig,
  the function outputs a value $\y$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct inspection.
  We sometimes abuse notation, and write $\trans[\uid]$ to mean that the \Inspect
  function is operating only for the obtain transcripts related to user \uid. 
\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
  \ldblbrace \gpk_i\rdblbrace_{i \in \Issuers})$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \y,
  obtained by applying \Inspect to the the signature \sig over message \msg. 
\end{description}

@@

\paragraph{Issuance, evaluation, and inspection functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are introduced to allow customized
governance of the resulting instantiation of an \UAS scheme. They will be
defined by different parties, but in all cases, they are run by users (maybe,
on user-private data). Also, in all cases, the user has to prove correctness of
their computation. We introduce them next, \todo{and will give concrete examples
  in \secref{sec:uac-instantiation}.}

\begin{description}
\item[$\fissue: (\upk, \attrs,\scred) \rightarrow 0/1$.] Defined by issuers,
  governs what customized conditions an issuer requires in order to issue
  credentials, when receiving a request from user with public key \upk, for
  attributes \attrs. \fissue may run checks on a (possibly empty) set of
  additional credentials \scred, which may further be used for blind issuance
  \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept a request, $0$ to
  reject it.  
\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Can be defined by any party,
  although we anticipate that this will typically be done by either singers,
  verifiers, or some governance organization. It defines customized conditions
  to be met by the owner of a user key \upk and set of credentials \scred, in
  order to sign a concrete message \msg. Returns $1$ to allow the signing,
  or $0$ to disallow it.
\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credentials, signed
  message, and produced signature (or a subset thereof), should be extractable
  by the group inspector.
\end{description}

\paragraph{Helper Function \Identify.} In addition, we make use of a helper
function \Identify for some of our definitions. This function receives
a signature and a user secret key, and determines whether the latter was used
to produce the former. This is in line with previous works on DAA
\cite{bfg+11,cdl16} and group signatures without traditional open functions
\cite{dl21,fgl21,gl19}. More concretely, the \Identify function, defined as $1/0
\gets \Identify(\usk,\sig)$, conveys meaning to our non-frameability definition
conditioned on the fact that, given a signature \sig accepted by \Verify,
\Identify returns $1$ for exactly one \usk.

\paragraph{Global Variables.} %
The environment manages several global variables in the games posed to the
adversary. Users are referred to with user identifiers, \uid; for credentials,
we use \cid; for groups, \gid. For credentials and groups, we use bold font to
denote sets: i.e., \scid and \sgid denot sets of credential and group
identifiers. All tables/sets are initialized as empty tables/sets, denoted
with $\emptyset$.

\begin{description}
\item[Tables for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers.
    Since we assume only one issuer per group, they are sets of {\gid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors.
    Since we assume only one inspector per group, they are sets of {\gid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$.
    To refer to the key pair of a specific user, we use $\UK[\uid]$. \PUBUK
    is a shorthand to refer to the public part, and \PRVUK refers to the
    private part -- we may also index both by \uid.
  \item[\IK, \PUBIK and \PRVIK.] Same as \UK, but for issuer key pairs. In
    addition, \IK also includes the \fissue function, which is part of the
    public key.
  \item[\OK, \PUBOK, \PRVOK.] Same as \UK, but for inspector key pairs. In
    addition, \OK also includes the \finsp function, which is part of the
    public key.
  \item[\GK.] We bundle public keys for issuers and inspectors into a common
    public key for each group. We use the table \GK for that purpose which,
    consequently, can also be indexed by \gid.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores credentials obtained by honest users. Thus, it is
    indexable by \cid. However, we slightly abuse notation and also use
    $\CRED[\uid]$ as a shorthand for all credentials obtained by honest user
    \uid, or $\CRED[\scid]$ to refer to a set of credentials with the
    identifiers in set \scid.
  \item[\OWNR.] Keeps track of which \uid is the owner of credentials obtained
    by honest users; i.e., $\OWNR[\cid]$ returns the \uid that obtained
    credential with identifier \cid.
  \item[\ATTR.] Keeps track of the attributes assigned to a credential, as well
    as the credential identifiers used to attest for any arbitrary claims
    required for issuance. This table can be indexed by credential identifier
    \cid.
  \item[\GRP.] Keeps track of the group to which a credential belongs to; i.e.,
    the group of the issuer who issued the credential. This table can be indexed
    by credential identifier \cid.
  \end{description}
\item[STables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users.
  \item[\CSIG.] Maintains challenge signatures, generated via the \CHALb oracle,
    by one of the challenge users in the anonymity game.
  \end{description}
\end{description}

\paragraph{Oracles.} %
Oracles are the interface of the adversary with the corresponding games. In
other words: through these oracles, the game environment exposes to the adversary
functionality that could otherwise be executed only by honest parties with
private knowledge -- knowledge that would make the adversary capable of
trivially breaking the security properties formalized in the experiments.
In the game-based definitions of our \UAS model, we leverage the following
oracles, which are formally defined in \figref{fig:oracles1} and
\figref{fig:oracles2}.

@@

        \procedure{$\IGEN(\gid,\fissue)$}{%
          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\gid] \gets ((\ipk,\fissue),\isk) \\
          \HI \gets \HI \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets ((\ipk,\fissue),\cdot) \\
          \pcreturn \ipk \\
        }

@@

        \procedure{$\OGEN(\gid,\feval,\finsp)$}{%
          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\gid] \gets ((\opk,\finsp),\osk) \\
          \HO \gets \HO \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets (\cdot,(\opk,\finsp)) \\
          \pcreturn \opk \\
        }

@@

        \procedure{$\ISSUE(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \\
          \hspace*{45pt}
          \Issue(\PRVIK[\gid],\PUBUK[\uid], \attrs,
          \ldblbrace \GK[\sgid] \rdblbrace) \rangle \\
          \trans[\cid] \gets \utrans;~\GRP[\cid] \gets \gid \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
          \pcreturn \top \\          
        }

        \procedure{$\OBTAIN(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\attrs, 
          \ldblbrace \CRED[\scid] \rdblbrace), \\
          \hspace*{50pt} \adv \rangle \\
          \CRED[\cid] \gets \cred;~\GRP[\cid] \gets \gid \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTISS(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\attrs,
          \ldblbrace \CRED[\scid] \rdblbrace), \\
          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],\attrs,
          \ldblbrace \GK[\sgid] \rdblbrace ) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\attrs) \\
          \GRP[\cid] \gets \gid \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\uid,\msg,\feval,\ldblbrace\scid\rdblbrace )$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\PRVUK[\uid],\msg,\ldblbrace\CRED[\scid]\rdblbrace) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\sig,\msg,\feval,\scid) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\CHALb(\uid_{0,1},\msg,\feval,
          \ldblbrace (\cscid_{0,1},\sgid) \rdblbrace))$}{%          
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
          \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
          \pcind \feval(\PUBUK[\uid_1],\CRED[\scid_1],\msg):
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\feval, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b]) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\feval,\cscid_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

    \caption{Detailed oracles available in our model (2/2). Oracles for
      obtaining credentials, signatures, and processing them.}
    \label{fig:oracles2}
  \end{figure*}
}

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced through a (set of)
credentials obtained by an honest user interacting with honest issuer(s), with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
    \sig \gets \Sign(\PRVUK[\uid],\msg,\feval,
    \ldblbrace \CRED[\scid] \rdblbrace ) \\
    \pcif \Verify(\sig,\msg,\GK[\sgid]) = 0: \pcreturn 1~
    \pccomment{\sig fails to verify} \\
    \pcif \CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)
    = 0: \pcreturn 1~
    \pccomment{Some \cid should not have been issued} \\
    \pcif \CorrectEval(\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
    = 0: \pcreturn 1~
    \pccomment{\msg should not have been signed}\\
    \pcif \CorrectInspect(\uid,\msg,\ldblbrace \scid \rdblbrace,
    \sig) = 0: \pcreturn 1~
    \pccomment{Some inspection of \sig is invalid}\\
    \pcreturn 0 \\
  }

  \procedure{$\CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)$}{
    \forall \cid \in \scid~\textrm{parse}~\ATTR[\cid]~\textrm{as}~
    (\scid^\cid,\attrs^\cid) \\
    \forall \gid \in \GRP[\scid]~\textrm{parse}~\GK[\gid]~\textrm{as}~
    ((\cdot,\fissue^\gid),\cdot) \\        
    \pcif \exists \cid \in \scid, \gid \in \GRP[\scid]~\st~
    \fissue^\gid(\PUBUK[\uid],\attrs^\cid,\CRED[\scid]^\cid) = 0: 
    \pcreturn 0 \\
    \pcreturn 1 \\   
  }
